Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2021-04-16 manuscript/manuscript.Rmd
Add explicit singlespacing for tables for manuscript template
Suparna's initial R&R additions

In 2016, Human Rights Watch claimed that civil society was under more aggressive attack than at any time in recent memory [@Roth:2016]. Governments across the globe have cracked down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017; @DPR:2015; @DPR:2016].[^NGOdef] As part of this phenomenon, NGOs face strong legal and bureaucratic obstacles to their work. Legal restrictions, or what we refer to as legal crackdowns, are a core part of these efforts. These crackdowns create barriers to entry, funding, and advocacy for NGOs in an effort to control, obstruct, and repress these organizations.

As a result of these legal crackdowns, foreign aid channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018]. While this has negatively impacted funding flows from public organizations like the United States Agency for International Development (USAID) and the Organisation for Economic Cooperation and Development (OECD), philanthropy from private donors and foundations is not as adversely affected [@McGill:2018]. Given this trend of closing civic space, INGOs need to maintain access to multiple sources of funding, including individual donors.

Individual private donations are a critical source of INGO funding. Total private philanthropy in the United States has grown substantially over time, reaching more than \$400 billion in 2018 (@fig:giving-aggregate). In 2018, private giving to NGOs working in international affairs reached \$22.08 billion, and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019]. But relying on individual donors means that NGOs must consider their preferences when fundraising. Which individual donor characteristics and attributes are most salient for INGOs interested in maximizing philanthropy at a time when they are facing increasingly hostile environments abroad? What kinds of donors consider an INGO's host country political environment when making the decision to donate?

![Aggregate philanthropic giving in the United States, 1977–2017. Source: Giving USA.](output/figures/giving_aggregate.pdf){#fig:giving-aggregate}

There exists a robust scholarship on the determinants of individual-level philanthropy to domestic causes. But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Motivating individuals to donate to international causes is hard as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100]. And research on the determinants of philanthropy for international causes—particularly towards organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013]. While previous work has looked at how organizational attributes of nonprofits affect donors' willingness to donate internationally [@ChaudhryHeiss:2020], we have yet to uncover demographic traits and experiences that motivate or deter individuals to donate during shrinking civic space.

We explore this question using a simulated market for philanthropic donations, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity. We adapt methods used in marketing to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes. We find that specific individual characteristics help shape donor preferences for donating to INGOs, and that an organization's target issue area and its relationship with its host government interact strongly with these characteristics. Personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism prefer donating to human rights organizations that have friendly relationships with their host governments. In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with more contentious relationships with host governments. Instead, they prefer donating to NGOs with friendly host-country relationships and working on less contentious issues like emergency response and refugee relief. Personas with higher trust are more comfortable donating to legally besieged INGOs.

This study contributes both to scholarship and practice in public policy, nonprofits, and philanthropy. Individual giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in the global distribution of income. Knowledge of demographic traits and its impact on funding can help nonprofits craft more effective and targeted marketing strategies [@Rajan:2009, 414]. Most NGOs working internationally have previously relied on government and foundation funding. But with shrinking civic space, these groups may need to readjust their fundraising strategies towards individuals. Framing is important in this regard—how people process information affects their willingness to donate.[^framing] However, existing research is unclear about which frames are effective when making appeals to individual donors considering international philanthropy. Since our study looks at multiple organizational and host country factors, our results can help NGOs frame their appeals.

More broadly, while research in public policy examines giving to NGOs, philanthropy is not seen as relevant by international relations as a discipline [@youde2019]. However, philanthropy—particularly donations received by INGOs—can help us understand changes in the dynamics of global governance. Private individuals exercise power and influence in unique ways that differ from other non-state actors. As @youde2019 [p. 44] points out, it changes our conceptions of individuals being passive recipients to active entities that are not merely objects of governance. Thus, it can shed light on the changing logic of global governance.

@@

# Sustaining civil society organizations abroad

Foreign aid to civil society—and NGOs in particular—has steadily increased over time. Many government and foundation donors perceive NGOs as nimbler and less bureaucratic than governments. In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013]. However, a restricted NGO environment merits examination of the diverse array of funds available to these organizations.

## Sources of funding

Thousands of INGOs in the Global South receive funds from a variety of public and private sources each year. Public funds—or traditional donor aid—channel money from official aid agencies through a variety of bilateral and multilateral institutions. Private sources include foundations, private corporations, and individuals. While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles from a funding perspective. Official donors have reduced the amount of aid channeled to countries with legal restrictions [@DupuyPrakash:2018] and have redirected funds within restrictive countries, decreasing funds for politically sensitive causes in favor of tamer issues that are more compatible with the governments of those countries [@ChaudhryHeiss:2018]. However, private funding towards international nonprofits has not been as adversely affected. Many foundations have continued channeling funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].

The advent of funding restrictions on NGOs globally and a subsequent decline in government and foundation funding has made the role and value of individual philanthropy in sustaining NGOs even clearer.[^phildef] NGOs need access to a diverse array of funds and individual donations to international affairs organizations have steadily increased over the past two decades. Moreover, in the United States, donations from individuals have far outstripped foundation and corporate giving. In 2018, individual donations amounted to \$292 billion, compared to \$76 billion from foundations and \$20 billion from corporations [@NPT]. Given that a majority of research is restricted to elite high net-worth donors[^highnetworth] [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of small-scale donors as well.

## Key drivers of individual-level philanthropy

A vast literature on philanthropy looks at organizational-level factors that motivate individuals to donate [@TBPrakash:2017]. However, donation decisions are not determined solely by a recipient organization's characteristics. Donors have personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy. Substantial research has looked at the determinants of donating to local—rather than international—causes, including four main attributes: social capital, the role of higher education, levels of religiosity, and national group attachment.

@@

Religiosity is also a significant predictor of the likelihood and level of giving. People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform to group and community standards [@wiepking2010]. Regular attendance may also strengthen individuals' beliefs in organizations' missions.

Finally, recent research looks at how a sense of ethnonationalism and national group attachment affects the decision to donate to domestic and international charities. Looking at UK respondents, @hartrobson2019 find that whereas nationalists have a preference for domestic charities, they are not necessarily averse to donating to international causes, whereas internationalists have a strong preference for donating to groups working abroad.

Which of these characteristics matter when deciding to donate to an INGO, particularly when an organization faces legal crackdown abroad? Overall, individuals with higher levels of income, education, and greater religious proclivities are not only more likely to give internationally, but also give higher amounts [@Rajan:2009; @CasaleBaumann:2015]. Additionally, we posit that other related characteristics such as civic and associational engagement and social trust also influence the decision to donate.

@@

@@

@@

Personas across both levels of social trust are most likely to donate to organizations with friendly relationships with their host governments. However, those with higher trust are less likely to be deterred by poor host-country relationships, while those with low trust tend to not donate to organizations facing criticism or crackdown abroad. A friendly relationship with a host government may be a manifestation of a belief that charities behave properly and exert a positive influence on society. Once an organization faces criticism or crackdown, however, support deteriorates rapidly among personas with low social trust, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism. Personas with high levels of trust, on the other hand, seem to stick with legally besieged organizations and show them the benefit of the doubt. The global crackdown on NGOs thus sours NGOs' least trusting individual donors.

@@

The global crackdown on civil society and the consequent decline of official development assistance has made the role of philanthropy in sustaining INGOs clear. INGOs need access to multiple sources of funding, and the value of individual-level philanthropy is still relatively under-explored. While existing research has examined the impact of organizational-level factors on individual giving as well as giving to local causes, in this paper, we specifically look at the demographic traits of those who are likely to donate to INGOs facing hostile environments abroad. We find several important trends from our simulated market for philanthropy. On average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad. Donors who are less wealthy, follow the news less often, and do not travel, are more attracted to organizations working on less contentious like emergency response and refugee relief.

More importantly, we find that trust in political institutions and in charitable organizations matters substantially in shaping donor preferences. Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments. Personas with low social trust tend to be wary of negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations. This could imply who donors who are the most trusting and involved could remain supportive when charities face government criticism and crackdown. The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.

@@

[^exceptions]: For exceptions, see @Micklewright:2009 on the UK; @Rajan:2009 on Canada; @wiepking2010 on the Netherlands; @CasaleBaumann:2015 on the U.S.

@@

[^phildef]: We use philanthropy to connote voluntary giving by an individual or group to promote the common good. While it can include grants given by foundations and corporations to nonprofit organizations, our focus here is on individual giving.

[^framing]: Framing is the process through which actors present information to influence perceptions or behavior. Previous research has shown that which frames are employed can have a significant effect on individuals' attitudes and behaviors [@BenfordSnow:2000; @ChongDruckman:2007].

>>>>

In 2016, Human Rights Watch claimed that civil society was under more aggressive attack than at any time in recent memory [@Roth:2016]. Governments across the globe have cracked down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017; @DPR:2015; @DPR:2016].[^NGOdef] As part of this phenomenon, NGOs face strong legal and bureaucratic obstacles to their work. Legal restrictions, or what we refer to as legal crackdowns, are a core part of these efforts. These crackdowns create barriers to entry, funding, and advocacy for NGOs in an effort to control, obstruct, and repress these organizations. Barriers to funding are especially pervasive and restrict the ability of NGOs to secure financial resources. Restrictive states may prevent the transfer of foreign funds to NGOs based on the origin of these funds and which issues these funds can be used towards.

As a result of these laws, foreign aid (also referred to as public or official aid) channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018]. Aid from public organizations like the United States Agency for International Development (USAID) and the Organisation for Economic Cooperation and Development (OECD) has decreased following the passage and implementation of these laws. However, philanthropy from private donors and foundations is not as adversely affected [@McGill:2018]. Many foundations have continued channeling funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018]. Given this trend of reduced public aid following restricted legal environments for NGOs abroad, many INGOs may need to devote more resources to fundraise from individual donors.

Individual private donations are a critical source of INGO funding. While total private philanthropy[^phildef] in the United States has grown substantially over time, particularly notable is the fact that private giving to NGOs working in international affairs  and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving and reached \$22.08 billion in 2018 [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019]. But relying on individual donors means that NGOs must consider their preferences when fundraising. Which individual donor characteristics and attributes are most salient for INGOs interested in maximizing philanthropy at a time when they are facing increasingly hostile environments abroad? What kinds of donors consider an INGO's host country political environment when making the decision to donate?

There exists a robust scholarship on the determinants of individual-level philanthropy to domestic causes. But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Motivating individuals to donate to international causes is hard as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100]. Trust is an essential component for INGO sustainability and for many nonprofits, trust often translates into grants and donations [@coombs2007]. Geography often impedes donors' direct evaluation of their work and trust is one of the most influential criteria that private donors use when deciding which nonprofits to support [@prakash2010trust; @bekkers2003trust]. A lack of trust could be further fueled by legal trouble with the NGO host government—a dynamic that individuals may not wish to enter with their dollars. How does trust in NGOs influence individuals' preferences to donate, especially when groups face crackdown?

We explore this question using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity. We adapt methods used in marketing to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes. We find that specific individual characteristics help shape donor preferences for donating to INGOs, and that an organization's target issue area and its relationship with its host government interact strongly with these characteristics. Personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism prefer donating to human rights organizations that have friendly relationships with their host governments. In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with more contentious relationships with host governments. Instead, they prefer donating to NGOs with friendly host-country relationships and working on less contentious issues like emergency response and refugee relief. Personas with higher trust are more comfortable donating to legally besieged INGOs. Our findings imply that individual donors with high trust would continue remaining supportive of INGOs when they face criticism and crackdown from foreign governments. On the other hand, government crackdown, and more broadly, closing civic space, may further sour NGOs least trusting individual donors.

This study contributes both to scholarship and practice in public policy, nonprofits, and philanthropy in three important ways. The paper helps us understand how the international community and NGOs might respond to the phenomenon of closing civic space, which does not appear to be receding. Most NGOs working internationally have previously relied on government and foundation funding. But in the face of decreasing funds from official donors, our results show that INGOs can rely on individual donors, specifically, their most trusting donors, when groups face a hostile environment abroad. These findings lend support to previous literature arguing that trust matters only when individuals donate to organizations acting under great uncertainty or working towards difficult goals [@Wiepking:2010].

Second, knowledge of demographic traits and its impact on funding can help nonprofits craft more effective and targeted marketing strategies [@Rajan:2009, 414]. Our paper shows that in readjusting their fundraising strategies towards individuals, framing, or the process through which actors present information to influence perceptions, is particularly important [@chong2007framing]. Framing affects their willingness to donate. However, existing research is unclear about which frames are effective when making appeals to individual donors considering international philanthropy. Since our study looks at multiple organizational and host country factors, our results can help NGOs frame their appeals. In particular, our results show that NGOs may benefit from publicizing crackdown at least towards their most trusting donors.

Finally, while research in public policy examines giving to NGOs, philanthropy is not seen as relevant by international relations as a discipline [@youde2019]. However, philanthropy—particularly donations received by INGOs—can help us understand changes in the dynamics of global governance. Private individuals exercise power and influence in unique ways that differ from other non-state actors. As @youde2019 [p. 44] points out, it changes our conceptions of individuals being passive recipients to active entities that are not merely objects of governance. Thus, it can shed light on the changing logic of global governance.

@@

# Closing civic space and its impact on INGOs

Foreign aid to civil society—and NGOs in particular—has steadily increased over time. Many government and foundation donors perceive NGOs as nimbler and less bureaucratic than governments. In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013]. However, NGO-state relationships have evolved over time—in the 1950s and 60s, international assistance channeled through NGOs aimed at producing socio-economic change rather than political progress. But in the aftermath of the dissolution of the Soviet Union, many NGOs had the explicit goal of promoting democracy and bringing down authoritarian governments. Subsequently, many states perceive them as threatening and have sought to repress them.

LINE ABOUT EXTENT. This phenomenon can have three main impacts on INGOs. First, it has led to a reduction in resources and grants available to INGOs. Second, restrictive NGO laws can affect INGO programming by preventing organizations from working in certain issue areas, or at least by making it more burdensome to do so. To deal with this, some groups have adapted by changing the nature of their programming to appear less threatening to the repressive countries. Finally, in the worst-case scenario, this phenomenon can also lead to a loss in INGOs access to target countries—often also associated with the use of violence against INGOs and their employees. In this paper, we exlusively focus on the first dilemma—the reduction in INGO funding and possible responses to it.

## Changes in INGO funding

Thousands of INGOs in the Global South receive funds from a variety of public and private sources each year. Public funds—or traditional donor aid—channel money from official aid agencies through a variety of bilateral and multilateral institutions. Private sources include foundations, private corporations, and individuals. While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles from a funding perspective.

Closing civic space not just resulted in net losses of income to INGOs, particularly through official bilateral and multilateral aid [@DupuyPrakash:2018], it has also affected how and where funds are allocated. Following the passage of anti-NGO laws, official donors move funds away from contentious causes such as human rights, media, corruption, advocacy, among others, towards tamer and more regime-compatible causes such as health, education [@ChaudhryHeiss:2018]. The latter trend has also been exacerbated by a preference among donors working in official aid and the democracy promotion establishment to gradually increase funding directed towards tame causes, at the expense of more contentious causes. This is because many tame causes can have easily quantifiable, measurable outputs, which makes it clear to show a program’s effectiveness over time (Bush 2015).

We argue that individual private donors can help fill in an important gap. Previous research has shown that individual donors do not use the same performance-based metrics as official donors [@desaikharas]. Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization’s issue area, mission, vision, and values and seek out supplementary information from friends family, and acquaintances [@CrosonShang:2011a; @TBPrakash:2017; @SzperPrakash:2011]. Due to these differences, we argue that individual donors can help address some of the challenges arising from reduced public funding available to INGOs. To be clear, we are not arguing that giving by individual donors would be a perfect substitute for NGOs net loss of income or income for certain programs, but rather, an important supplement to reduced funding from foreign sources. Moreover, it would also be a supplement to private funding from foundations towards international nonprofits which has not been as adversely affected, with foundations continue to channel funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].

However, research on the determinants of individual-level philanthropy for international causes—particularly towards organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013]. Moreover, a majority of research on giving to international groups is restricted to elite high net-worth donors[^highnetworth] [@USTrust2014]. We still know little about demographic traits and experiences that motivate or deter individuals to donate during shrinking civic space. Below, we look at key drivers of individual-level philanthropy and show how the importance of trust in donating during civic crackdowns.

 the role of higher education, levels of religiosity, and trust.

@@

Religiosity is also a significant predictor of the likelihood and level of giving. People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform to group and community standards [@WiepkingBekkers:2010]. Regular attendance may also strengthen individuals' beliefs in organizations' missions.

Finally, an individual's disposition to trust, or the general tendency to trust others, including individuals groups or institutions has been shown to have an impact on both intention to donate as well as actual donation behavior. Trusting people are not only more likely to give to charitable causes, but also donate more [@BrownFerris2007].

Which of these characteristics matter when deciding to donate to an INGO, particularly when an organization faces legal crackdown abroad? Overall, individuals with higher levels of income, education, and greater religious proclivities are not only more likely to give internationally, but also give higher amounts [@Rajan:2009; @CasaleBaumann:2015]. Additionally, we posit that social trust can play an important role in the decision to donate, as individuals who trust NGOs are less likely than others to halt their monetary support in the face of difficulties [@dwyer1987].

@@

\stgroup

\singlespacing

@@

\fingroup

@@

Personas across both levels of social trust are most likely to donate to organizations with friendly relationships with their host governments. However, those with higher trust are less likely to be deterred by poor host-country relationships, while those with low trust tend to not donate to organizations facing criticism or crackdown abroad. A friendly relationship with a host government may be a manifestation of a belief that charities behave properly and exert a positive influence on society. Once an organization faces criticism or crackdown, however, support deteriorates rapidly among personas with low social trust, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism. When the risk of a certain action is higher, people need higher levels of confidence or trust to engage in that action [@coleman1990]. When NGOs have goals that are harder to accomplish (as is the case under shrinking civic space), there is greater uncertainty that the donated money will meaningfully contribute to the intended cause.

Personas with high levels of trust, on the other hand, seem to stick with legally besieged organizations and show targeted groups the benefit of the doubt. The global crackdown on NGOs thus sours NGOs' least trusting individual donors. Overall, our results support research that donors with high levels of trust are more active in giving than those with low levels of trust [@sargeant2008] and that trust especially matters when individuals donate to organizations working under great uncertainty and towards difficult goals [@Wiepking:2010].

@@

The global crackdown on civil society and the consequent decline of official development assistance has made the role of philanthropy in sustaining INGOs clear. INGOs need access to multiple sources of funding, and the value of individual-level philanthropy in sustaining the operations of groups working in challenging environments is still relatively under-explored. While trust is a difficult construct to define, the nonprofit literature conceptualizes trust as a key driver of commitment, which is shown to impact both intention to donate as well as actual donation behavior. When considering repressive environments and NGOs working on more difficult goals, a lack of trust could be further fueled by legal trouble with the NGO host government—a dynamic that individuals may not wish to enter with their dollars. How does trust in NGOs influence individuals' preferences to donate, especially when groups face crackdown?

Using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity, we find several important trends. Trust in political institutions and in charitable organizations matters substantially in shaping donor preferences. Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments. Personas with low social trust tend to be wary of negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations. This could imply who donors who are the most trusting and involved could remain supportive when charities face government criticism and crackdown. The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors. Our findings lend support to research showing that individuals who trust NGOs are more likely to continue their monetary support of NGOs in the face of difficulties and under great uncertainty [@dwyer1987; @Wiepking:2010].

In addition, we find that on average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad. Donors who are less wealthy, follow the news less often, and do not travel, are more attracted to organizations working on less contentious like emergency response and refugee relief.

@@

[^exceptions]: For exceptions, see @Micklewright:2009 on the UK; @Rajan:2009 on Canada; @WiepkingBekkers:2010 on the Netherlands; @CasaleBaumann:2015 on the U.S.

@@

[^phildef]: We use philanthropy to connote voluntary giving by an individual or group to promote the common good. While it can include grants given by foundations and corporations to nonprofit organizations, our focus here is on individual giving. Some perspectives see philanthropy as more of a strategic long-term practice that seeks to address the root causes of issues, and charity as a more short-term practice focused on providing immediate relief. But many scholars see philanthropy as essentially synonymous with charitable donations, as the latter can also address longer-term or strategic isssues [@Castle:2004]. As such, despite these subtle differences, we use the terms inter-changeably here both because previous literature does so, and because in the case of philanthropic or charitable-giving to NGOs during crackdown, individuals could be giving to nonprofits both for immediate relief as well as long-term strategic purposes.
